### 2025-07-20 evaluating-prediction-accuracy.qmd
20250720 - accuracy of seasonal versus weekly projections

>>>>

Prediction accuracy tended to be higher for seasonal projections than for weekly projections—likely because of the greater number of "trials" (i.e., plays) in a season compared to a game, so more of the random error averages out.
The weaker accuracy weekly projections makes betting on daily fantasy sports a gamble.
